SPIN Novelty

### 2019-04-23 stats/kids_novelty.Rmd
update kids novelty model

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date))

@@

## sanity checks
d %>%
  group_by(experiment,subage) %>%
  summarise(n = length(unique(subid)))

@@

# maximal converging model
bm <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
          data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(bm)

>>>>

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date),
         subid = ifelse(subid =="190422_6_nov,","190422_6_nov",subid),
         subage = ifelse(subid =="190422_2_nov","4",subage))

@@

## sanity checks
d %>%
  group_by(experiment,subage) %>%
  summarise(n = length(unique(subid)),
            data_points = n())

@@

# maximal converging model
bm_full <- brm(correct ~ age_num * experiment + (1 | subid) + (age_num * experiment | agent), 
          data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(bm_full)

bm_null <- brm(correct ~ age_num + (1 | subid) + (age_num * experiment | agent), 
          data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

summary(bm_null)

bayes_factor(bm_full, bm_null, log = F, maxiter = 5000)
